Ionization of biological molecules by multicharged ions using the stoichiometric model

### 2019-11-22 submit_jpb/response.txt

Referee 1:

We thank the referee for the comments on our manuscript. Please find below our reply to his/her observations.

The present work considers fully stripped ions. Indeed, this may be considered as a weakness of our calculations. Nonetheless, we plan to extend our theoretical approach to partially stripped ions in the future.

Detailed reply:

1) We have changed the wording of our findings in the corresponding sections.

2) The grammatical error was corrected.

3a) The dependence of the mean energy with the projectile charge at intermediate energy reflects the non-linear dependence on E and ZP of the continuum state in the CDW approximation. Then, the dependence of the numerator and the denominator on ZP is not canceled out, which explains the maximum in Fig. 2. On the contrary, the behavior at high energy follows the Z^2 rule, and the mean energy distribution tends to a universal value for all ions, as noted on page 3.
3b) We included a few sentences discussing the usefulness of understanding the relationship between the mean energy and angle distribution of secondary electrons with the radiation damage.

4) The denominator in Eq. 4 is the same as in Eq. 3: the total cross-section. They are both integrated on different variables. We have included the expression of the normalization of the angular distribution.

5) We defined the dotted line accordingly.

6a) We included the reference to Table I in the caption.
6b) In general, the curves within each scaling band are ordered from the smallest to the largest. For the hydrocarbons, this behavior holds for both scalings since n_e for carbon does not change. However, this is not always the case (see, for example, adenine C5H5N5, uracil C4H4N2O2, and DNA backbone C5H10O5P in Fig. 1 attached). 
6c) Upon the suggestion of the referee, we included the Toburen numbers in Table II. The inclusion of the band by Toburen, together with the new scaling, was too confusing and finally decided not to modify the figure.

7) We included the Toburen scaling in Fig. 2, attached. The x-axis 
refers to the number of active electrons, whether they are from the 
Toburen or the CDW scaling. As seen, the scaling by Toburen is not as good as ours, which follows Fig. 6. To avoid having too many curves, 
we decided not to modify Fig. 7, but we comment on these differences 
in the manuscript: "An equivalent plot using the Toburen numbers n_e of Table II does not exhibit the straight lines obtained with
the present scaling."

8) We appreciate the suggestion of the scaling with Z at intermediate energies. We check it for the molecules in Figs. 4 and 5. We decided to include a new figure for DNA bases. We will continue to investigate the scope and limitation of this scaling for different biological molecules.

Referee 2:

We decided to include in the introduction a comment about different previous work combining atomic cross sections to obtain molecular ones by Galassi et al. and Ludde et al.
"Different approaches have been proposed to deal with the ionization of molecular targets within the independent atom model. For example, Galassi et al. [1] obtain molecular cross sections by combining CDW-EIS atomic ones based on the population of the molecular orbitals. Much more recently, Ludde et al. [2, 3] propose a combination of atomic cross sections with geometrical screening correction."

### 2019-11-22 ionmol_stoi.tex
include C6+ reference to manuscript

The damage caused by the impact of multicharged heavy projectiles on 
biological targets has become a field of interest due to its recent 
implementation in ion--beam cancer therapy. The effectiveness of the 
radiation depends on the choice of the ions. In particular, theoretical 
and experimental studies with different projectiles have concluded that 
charged carbon ions could be the most suitable ions to be used. 
Nonetheless, the study of such systems represents a challenge from the 
theoretical point of view.

@@

@@

\bibitem{miraglia2019} 
J. E. Miraglia. Shell-to-shell ionization cross
sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
O$^{8+}$ on H, C, N, O, P, and S atoms (to be published).

\bibitem{surdutovic2018} 
Multiscale approach to the physics of radiation
damage with ions. E. Surdutovich and A. V. Solov'yov, 
arXiv:1312.0897v, (2013)

\bibitem{abril2015} 
P. de Vera1, I. Abril, R. Garcia-Molina and
A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
for radiobiological applications. 
Journal of Physics: Conference Series \textbf{438}, 012015 (2013).

>>>>

The damage caused by the impact of multicharged heavy projectiles on 
biological targets has become a field of interest due to its recent 
implementation in ion--beam cancer therapy. The effectiveness of the 
radiation depends on the choice of the ions. In particular, theoretical 
and experimental studies with different projectiles have concluded that 
charged carbon ions could be the most suitable ions to be used~\cite{Mohamad2017}. 
Nonetheless, the study of such systems represents a challenge from the 
theoretical point of view.

@@

\bibitem{Mohamad2017}
O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, A. J. Davis, D. N. Kim, 
Carbon Ion Radiotherapy: A Review of Clinical Experiences and Preclinical Research, with an Emphasis on DNA Damage/Repair. 
Cancers \textbf{9}, 66 (2017).

@@

\bibitem{miraglia2019} 
J. E. Miraglia,
Shell-to-shell ionization cross sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
O$^{8+}$ on H, C, N, O, P, and S atoms (to be published).

\bibitem{surdutovic2018} 
E. Surdutovich and A. V. Solov'yov, 
Multiscale approach to the physics of radiation damage with ions. 
arXiv:1312.0897v, (2013)

\bibitem{abril2015} 
P. de Vera1, I. Abril, R. Garcia-Molina and
A. V. Solov'yov,
Ionization of biomolecular targets by ion impact: input data for radiobiological applications. 
Journal of Physics: Conference Series \textbf{438}, 012015 (2013).
